Milk intake and risk of mortality risk

### 2020-06-12 Paperfolder/Paperfolder.Rmd
updated names of the authors

---
title: Milk intake and risk of mortality risk 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: John Doe
    affil: 2, \dagger, \ddagger
affiliation:
  - num: 1
    address: |
      Muenster University of Applied Sciences - 
      Institute for Infrastructure, Water, Resources, Environment
      Correnstr. 25, 48149 Muenster, Germany
    email: leutnant@fh-muenster.de
  - num: 2
    address: |
      Your department
      Street, City, Country
    email: mail@mail.com
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: water
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

# Version

This Rmd-skeleton uses the mdpi Latex template published 2019/02. 
However, the official template gets more frequently updated than the 'rticles'
package. Therefore, please make sure prior to paper submission, that you're 
using the most recent .cls, .tex and .bst files 
(available [here](http://www.mdpi.com/authors/latex)).

>>>>

---
title: Milk intake and risk of mortality risk 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: mybibfile.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

<!-- # Version -->

<!-- This Rmd-skeleton uses the mdpi Latex template published 2019/02.  -->
<!-- However, the official template gets more frequently updated than the 'rticles' -->
<!-- package. Therefore, please make sure prior to paper submission, that you're  -->
<!-- using the most recent .cls, .tex and .bst files  -->
<!-- (available [here](http://www.mdpi.com/authors/latex)). -->

### 2020-06-12 Paperfolder/Paperfolder.tex
updated names of the authors

% Authors, for the paper (add full first names)
\Author{Chaochen
Wang$^{1,*}$\href{https://orcid.org/0000-0001-5533-1497}{\orcidicon}, Hiroshi
Yatsuya$^{2}$, Yingsong Lin$^{1}$, $^{}$}

% Authors, for metadata in PDF
\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, }

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Muenster University of Applied Sciences - Institute for
Infrastructure, Water, Resources, Environment Correnstr. 25, 48149
Muenster,
Germany; \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}}\\
$^{2}$ \quad Your department Street, City,
Country; \href{mailto:mail@mail.com}{\nolinkurl{mail@mail.com}}\\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}};
Tel.: +XX-000-00-0000.}

% Current address and/or shared authorship
\firstnote{Current address: Updated affiliation}
\secondnote{These authors contributed equally to this work.}

@@

% Simple summary
\simplesumm{A Simple summary goes here.}

@@

\hypertarget{version}{%
\section{Version}\label{version}}

This Rmd-skeleton uses the mdpi Latex template published 2019/02.
However, the official template gets more frequently updated than the
`rticles' package. Therefore, please make sure prior to paper
submission, that you're using the most recent .cls, .tex and .bst files
(available \href{http://www.mdpi.com/authors/latex}{here}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short
paragraph specifying their individual contributions must be provided.
The following statements should be used ``X.X. and Y.Y. conceive and
designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
analyzed the data; W.W. contributed reagents/materials/analysis tools;
Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state `The authors
declare no conflict of interest.' Authors must identify and declare any
personal circumstances or interest that may be perceived as
inappropriately influencing the representation or interpretation of
reported research results. Any role of the funding sponsors in the
design of the study; in the collection, analyses or interpretation of
data in the writing of the manuscript, or in the decision to publish the
results must be declared in this section. If there is no role, please
state `The founding sponsors had no role in the design of the study; in
the collection, analyses, or interpretation of data; in the writing of
the manuscript, an in the decision to publish the results'.}

@@

\input{"appendix.tex"}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds \ldots\ldots{} are
available from the authors.}

>>>>

% Authors, for the paper (add full first names)
\Author{Chaochen
Wang$^{1,*}$\href{https://orcid.org/0000-0001-5533-1497}{\orcidicon}, Hiroshi
Yatsuya$^{2}$\href{https://orcid.org/0000-0002-6220-9251}{\orcidicon}, Yingsong
Lin$^{1}$\href{https://orcid.org/0000-0003-0214-3649}{\orcidicon}, Shogo
Kikuchi$^{1}$\href{https://orcid.org/0000-0001-9499-9668}{\orcidicon}, Tae
Sasakabe$^{1}$\href{https://orcid.org/0000-0002-7417-5693}{\orcidicon}, Sayo
Kawai$^{1}$\href{https://orcid.org/0000-0002-5156-4880}{\orcidicon}, Hiroyasu
Iso$^{3}$\href{https://orcid.org/0000-0002-9241-7289}{\orcidicon}, Akiko
Tamakoshi$^{4}$\href{https://orcid.org/0000-0002-9761-3879}{\orcidicon}}

% Authors, for metadata in PDF
\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Shogo
Kikuchi, Tae Sasakabe, Sayo Kawai, Hiroyasu Iso, Akiko Tamakoshi}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Public Health, Aichi Medical University
School of Medicine, Nagakute, Japan; \\
$^{2}$ \quad Departmet of Public Health, Fujita Health University School
of Medicine, Toyoake, Japan; \\
$^{3}$ \quad Public Health, Department of Social Medicine, Osaka
University Graduate School of Medicine, Osaka, Japan; \\
$^{4}$ \quad Department of Public Health, Faculty of Medicine, Hokkaido
University, Sapporo, Japan; \\
}
% Contact information of the corresponding author
\corres{Correspondence: Email.:
\href{mailto:chaochen@wangcc.me}{\nolinkurl{chaochen@wangcc.me}}; Tel.:
+81-561-62-3311. Department of Public Health, Aichi Medical University
School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan
(C.W.)}

% Current address and/or shared authorship

@@

% Simple summary

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{``X.X. and Y.Y. conceive and designed the
experiments; X.X. performed the experiments; X.X. and Y.Y. analyzed the
data; W.W. contributed reagents/materials/analysis tools; Y.Y. wrote the
paper.'\,'}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{The authors declare no conflict of interest. The
founding sponsors had no role in the design of the study; in the
collection, analyses, or interpretation of data; in the writing of the
manuscript, an in the decision to publish the results.}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
